%%
%%    ATerm -- The ATerm (Annotated Term) library
%%    Copyright (C) 1998-2000  Stichting Mathematisch Centrum, Amsterdam, 
%%                             The  Netherlands.
%%
%%    This program is free software; you can redistribute it and/or modify
%%    it under the terms of the GNU General Public License as published by
%%    the Free Software Foundation; either version 2 of the License, or
%%    (at your option) any later version.
%%
%%    This program is distributed in the hope that it will be useful,
%%    but WITHOUT ANY WARRANTY; without even the implied warranty of
%%    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%%    GNU General Public License for more details.
%%
%%    You should have received a copy of the GNU General Public License
%%    along with this program; if not, write to the Free Software
%%    Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307 USA
%%
\documentclass{article}

%{{{ LaTeX configuration

\usepackage[english]{babel}
\usepackage{epsfig}
\usepackage{latexsym}
\usepackage{spec/ASF+SDF}
\usepackage{spec/ASF+SDF-options}

\newcommand{\ATerm}{ATerm}
\newcommand{\ATerms}{ATerms}
\newcommand{\AFun}{AFun}
\newcommand{\AFuns}{AFuns}
\def\metaenv{Meta-En\-vir\-on\-ment}
\def\asmetaenv{{\sc Asf+Sdf}\ Meta-En\-vir\-on\-ment}
\def\aterms{\mbox{ATerms}}
\def\aterm{\mbox{ATerm}}
\def\asfix{\mbox{\sc AsFix}}
\def\sdf{\mbox{\sc Sdf}}
\def\asf{\mbox{\sc Asf}}
\def\asdf{\mbox{\sc Asf+Sdf}}
\def\ascii{\mbox{\sc Ascii}}
\def\TB{ToolBus}

\newcommand{\baf}{BAF}

%}}}

%{{{ Title page

\title{Efficient Annotated Terms}
\author{M.G.J. van den Brand$^{^1}$\\
        H.A. de Jong$^{^2}$\\
        P. Klint$^{1,2}$\\
        P.A. Olivier$^{^2}$\\
        \vspace{.1cm}\\
        {\small\sl $^1$CWI,
        Department of Software Engineering\vspace{-.2cm}}\\
        {\small\sl Kruislaan 413, 1098 SJ Amsterdam, The Netherlands}
        \vspace{.1cm}\\
        {\small\sl $^1$University of Amsterdam,
        Programming Research Group\vspace{-.2cm}}\\
        {\small\sl Kruislaan 403, 1098 SJ Amsterdam, The Netherlands}
        %%\vspace{.1cm}\\
        %%{\small \sl\tt Mark.van.den.Brand@cwi.nl, jong@wins.uva.nl, Paul.Klint@cwi.nl, olivierp@wins.uva.nl}
}

\begin{document}
\maketitle

%}}}

%{{{ Abstract

\begin{abstract}
How do distributed applications exchange tree-like data structures?  
We introduce the abstract data type of \emph{Annotated Terms}
(\emph{ATerms}) and discuss their design, implementation and
application.  A comprehensive procedural interface enables
creation and manipulation of ATerms in C or Java.  
The ATerm implementation is based on maximal subterm
sharing and automatic garbage collection.  
A binary exchange format for the
concise representation of ATerms (sharing preserved) allows the
fast exchange of ATerms between applications.  In a typical
application---parse trees which contain considerable redundant 
information---less than 2 \emph{bytes} are needed to represent 
a node in memory,
and less than 2 \emph{bits} are needed to represent it in binary format. 
The implementation of ATerms scales up to the manipulation
of ATerms in the giga-byte range.
\end{abstract}

%}}}

\input{aterm.ltx}

%%\acks
\section*{Acknowledgments}

We want to thank all current users of the \ATerm\ library.
Special thanks to Jan-Friso Groote (for his input and sometimes
severe requirements, and his implementation of the ATermTable 
and ATermIndexedSet related functionality) and to 
Merijn de Jonge and Jeroen Scheerder
(for detecting a large number of intricate bugs).
We thank Alexander van den Bergh for porting the \ATerm\ library
to Windows/NT as part of his Master thesis project, and
Joost Visser for providing us with useful information on ASDL and
for writing a tool to pickle \aterms.
We thank Pierre-Etienne Moreau for the fruitful
discussions on this subject during his stay in Amsterdam.
Finally, we want to thank the anonymous referees for their
constructive remarks.

\bibliographystyle{alpha}
\bibliography{thesis}

\input{append.ltx}

\end{document}
