%%
%%    ATerm -- The ATerm (Annotated Term) library
%%    Copyright (C) 1998-2000  Stichting Mathematisch Centrum, Amsterdam, 
%%                             The  Netherlands.
%%
%%    This program is free software; you can redistribute it and/or modify
%%    it under the terms of the GNU General Public License as published by
%%    the Free Software Foundation; either version 2 of the License, or
%%    (at your option) any later version.
%%
%%    This program is distributed in the hope that it will be useful,
%%    but WITHOUT ANY WARRANTY; without even the implied warranty of
%%    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%%    GNU General Public License for more details.
%%
%%    You should have received a copy of the GNU General Public License
%%    along with this program; if not, write to the Free Software
%%    Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307 USA
%%
\documentclass{article}
\title{Corrections to ``Efficient Annotated Terms''\\
Second round}
\author{M.G.J. van den Brand\\
        H.A. de Jong\\
        P. Klint\\
        P.A. Olivier}

\begin{document}

\maketitle
Our paper \emph{Efficient Annotated Terms} by M.G.J. van den Brand,
H.A. de Jong, P. Klint and P.A. Olivier has been submitted to SPE.
After reviewing we have received  and responded to the referee's reports.
The resulting improved version of the paper has been resubmitted and 
in this note we give a detailed response to the remaining comments
on this improved version.

\section*{Comments on the issues raised by the referee}

All small textual modifications proposed by the referee and
indicated in the paper copy have been applied.

\begin{itemize}

\item[1.] Remark on terminology.

\emph{We agree that the terminology with respect to sharing
could be improved. We adopted the terminology proposed by
the referee and we have adapted at several points the text
and introduced the term ``in-memory'' sharing.}

\item[2.] Design of Figure 3.

\emph{We did various experiments to improve the layout of Figure
3. The referee proposes a ``log scale'' but the effect is even
worse and does not improve the readability of the figure. 
So we stick to the current layout.}

\item[3.] Verboseness on garbage collection.

\emph{We have rewritten this section and it has become more concise.}

\item[4.] Remark on using S-expressions in the measurement.

\emph{We have written a conversion program and added figures
on S-expressions.}

\item[5.] Previous work on substructure sharing for in-memory representation.

\emph{We added a short section to Related work on hash consing.}

\item[6.] Literature on Binary file format.

\emph{We did not find any relevant literature on this subject. Although
we have to be honest and confess we did not perform an exhaustive search.}

\end{itemize}


\end{document}
